\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-01 draft.tex
rewrite leg part of sec:choices

Notice that, aside from the endogeneity of the weight the legislature places on the lobbying industry's profits, this is precisely the \textit{deus ex machina} government objective function popularized by Baldwin (1987) that is commonly employed in the literature on the political economy of trade agreements. Since trade policies are overwhelmingly determined within the context of trade agreements, it is useful to have a framework to bring together the endogenous political pressure of PFS-style modeling with the trade agreements approach; the formulation in Equation~\ref{eq:ml} is intended as a bridge between the two. Buzard (2016) for an example of how this form can be used to integrate the analysis of endogenous political activity and exogenous shocks to the political welfare of governments.

the weight the median legislator places on the profits of the import-competing industry, $\ga(e,\ve)$, is affected by the level of lobbying effort and a random variable $\ta$. This allows for the analysis of endogenous lobbying to be integrated with the standard political economy shocks in the trade agreements literature. Alternatively, as motivated below, it can represent reduced-form modeling of political uncertainty arising from a complex decision-making process within a legislature. Modeling the objective function so closely on the standard in the trade agreements literature allows for direct comparisons to the large extant body of work that studies exogenous shocks only, revealing cleanly the effects of the addition of endogenous lobbying---and if one wants---this different kind of political uncertainty.

I allow for the possibility of this political uncertainty, which can be interpreted as uncertainty over the identity of the median legislator, in order to model the idea that the lobbying and voting ``game'' that goes on within legislatures is often complex enough that none of the actors know precisely what the outcome will be---that is, no one can predict exactly which legislator will be the median and therefore what weight will be placed on import-industry profits at the time of the vote. Thus one way we can think about $\ta$ is as an additional influence on the legislature's preferences about which all parties---executives, legislators and lobbies alike---are uncertain. It is this interpretation of $\ta$ I take throughout the paper.

>>>>

Notice that, aside from the endogeneity of the weight the legislature places on the lobbying industry's profits, Equation~\ref{eq:ml} is precisely the \textit{deus ex machina} government objective function popularized by Baldwin (1987) that is commonly employed in the literature on the political economy of trade agreements. Instead of the weight on profits being constant as in the exogenous case or necessarily linear in contributions as in the PFS case, this form allows for both endogeneity and non-linearity.

Since trade policies are overwhelmingly determined within the context of trade agreements, it is useful to have a framework to bring together the endogenous political pressure of PFS-style modeling with the trade agreements approach. The formulation in Equation~\ref{eq:ml} is intended as a bridge between the two. See Buzard (2016) for an example of how this form can be used to integrate the analysis of endogenous political activity and exogenous shocks to the political welfare of governments.

In addition, letting the weight the median legislator places on the profits of the import-competing industry $\ga(e,\ve)$ be affected by the level of lobbying effort as well a random variable $\ta$ allows for the analysis of endogenous lobbying to be integrated with the standard political economy shocks of the trade agreements literature. Modeling the objective function so closely on the standard in the trade agreements literature allows for direct comparisons to the large extant body of work that studies exogenous shocks only, revealing cleanly the effects of the addition of endogenous lobbying---and if one wants---this different kind of political uncertainty.

Alternatively, the integration of the random variable $\ta$ can represent reduced-form modeling of political uncertainty arising from a complex decision-making process within a legislature. One can interpret $\ta$ as measuring uncertainty over the identity of the median legislator in order to represent the idea that the lobbying and voting ``game'' that goes on within legislatures is often complex enough that none of the actors know precisely what the outcome will be---that is, no one can predict exactly which legislator will be the median and therefore what weight will be placed on import-industry profits at the time of the vote. Thus one way we can think about $\ta$ is as an additional influence on the legislature's preferences about which all parties---executives, legislators and lobbies alike---are uncertain. It is this interpretation of $\ta$ I take throughout this paper.
